Polyester RNA-seq simulation study

### 2018-10-09 datasets/RNA-Seq/polyester-simulation.Rmd
Update authorship of polyester

---
title: "Polyester RNA-seq simulation study"
author: "Stephanie Hicks"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

>>>>

---
title: "Polyester RNA-seq simulation study"
author: "Stephanie Hicks & Keegan Korthauer"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---
